Left-Linear Rewriting in Adhesive Categories

### 2024-11-14 arxiv_concur/main.tex

  \bigskip
  \noindent
  (2) $j<i-1$ or $j>i-1$\\
  %
  In this case $\nu_1$ does not ``interfere'' with $\transp{i}$, i.e.~$i$ still satisfies the hypotheses of the lemma with respect to the
  switching sequence
  $\der{D}_1 \shift{\nu_2} \ldots \shift{\nu_n} \der{D}_n$.

@@

  Recall that $\der{D}_0 \shift{\nu_1} \der{D}_1$ and, given the
  working assumption (ii), the switches $\nu_1$ and $\transp{i}$ can
  be done in reverse order, thus getting, as desired
  \begin{center}
    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\nu_1} \ldots
    \shift{\nu_n'} \der{D}_n$
  \end{center}

@@

  By Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:1})
  we can reorganise the first three switchings as

>>>>

  \bigskip
  \noindent
  (2) $j<i-1$ or $j>i+1$\\
  %
  In this case $\nu_1$ does not ``interfere'' with $\transp{i}$, i.e.~$i$ still satisfies the hypotheses of the lemma with respect to the
  switching sequence
  $\der{D}_1 \shift{\nu_2} \ldots \shift{\nu_n} \der{D}_n$.

@@

  Recall that $\der{D}_0 \shift{\nu_1} \der{D}_1$ and, given the
  working assumption (2), the switches $\nu_1$ and $\transp{i}$ can
  be done in reverse order, thus getting, as desired
  \begin{center}
    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\nu_1} \ldots
    \shift{\nu_n'} \der{D}_n$
  \end{center}

@@

  By Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:1}) and (\ref{lem:indep-global-left:2})
  we can reorganise the first three switchings as
